### 2019-03-04 report/final-report.tex
moving lens section

\section{Lenses}\bcp{Is a separate section the best place for this?  Is
  this the kind of example we had in mind?  Is it OK that I cannibalized the
later subsection on lenses?  (We could alternatively move all this there.)}

@@

Before surveying our methods and results on synthesis, we quickly sketch an
example of what a lens looks like, using a simplified situation drawn from a
hypothetical U.S. company. In this company, management and human resources
(HR) store information about employees in separate text files: management
stores the names of employees and their salaries while HR stores the names
of employees and their health insurance
providers. Figure~\ref{fig:minimized-representations} gives examples of the
two file formats and regular expressions describing them.

@@

Our approach to lens synthesis combines two strategies.  First, as
illustrated in the previous section, we use \textit{domain-specific
  programming language}, specifically the Boomerang  language~\cite{boomerang,
  Matching10}, which is designed for writing bidirectional string
transformations.  Second, we exploit \textit{type- and example-directed
  program synthesis}, which uses enumerative techniques to search a space of
candidate solutions.  The search is constrained by the type information
about the program, as well as by example instances provided by the user.

>>>>

Our approach to lens synthesis combines two strategies.  First, 
we use a \textit{domain-specific
  programming language}, Boomerang~\cite{boomerang,Matching10},
which is designed for writing bidirectional string
transformations.  Second, we exploit \textit{type- and example-directed
  program synthesis}, which uses enumerative techniques to search a space of
candidate solutions.  The search is constrained by the type information
about the program, as well as by example instances provided by the user.

\subsection{Lenses}

@@

Before surveying our methods and results on synthesis, we quickly sketch an
example of what a Boomerang lens looks like, using a simplified situation drawn from a
hypothetical U.S. company. In this company, management and human resources
(HR) store information about employees in separate text files: management
stores the names of employees and their salaries while HR stores the names
of employees and their health insurance
providers. Figure~\ref{fig:minimized-representations} gives examples of the
two file formats and regular expressions describing them.

@@
